Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-05-03 paper.tex
Added figures according to categorize the methods into failure and succeed ones

The experimental results have been obtained from four different approaches:
1. Applying ALS technique (ALS)
2. Employing Bias as well as ALS technique (ALS-Bias)
3. Using just Bias (Bias)
4. Results stemmed from ommiting the impact of predicted value of canstant files 
In all above approaches, dummy classifier which makes predictions using simple rules\cite{URL}has been used to indicate that how much predicted value would tend to be anticipate as the dominent value of the utility matrix. This classifier is considered as an accuracy evaluator since the binary utility matrix is consist of \{1,0\} which respectively represent whether a difference has been observed between the same files in two different conditions (by comapring their checksums) or not.
With the knowledge of the fact that Random Unreal method is not applicable into our case study we used its results as the comparision between the unrealistic method and realistics ones. In this regard, the aformentioned approaches are propossed and tried to lessen the gaps between the best results from random-unreal and the applied one.

>>>>

The experimental results have been obtained from four different approaches:\\
1. Applying ALS technique (ALS)\\
2. Employing Bias as well as ALS technique (ALS-Bias)\\
3. Using just Bias (Bias)\\
4. Results stemmed from ommiting the impact of predicted value of canstant files \\
In all above approaches, dummy classifier which makes predictions using simple rules\cite{URL}has been used to indicate that how much predicted value would tend to be anticipate as the dominent value of the utility matrix. This classifier is considered as an accuracy evaluator since the binary utility matrix is consist of \{1,0\} which respectively represent whether a difference has been observed between the same files in two different conditions (by comapring their checksums) or not.
With the knowledge of the fact that Random Unreal method is not applicable into our case study we used its results as the comparision between the unrealistic method and realistics ones. In this regard, the aformentioned approaches are propossed and tried to lessen the gaps between the best results from random-unreal and the applied one.
